### 2023-04-16 paper/language.tex
remove 'lift' constructor
Some description of the layout value introduction syntax and how parameters and variable freshness works for it

@@

\subsection{\Pika{} Syntax}
\begin{align*}
  &e ::= \cdots \mid \apply_{\alpha}(e) \mid \liftExpr_{\alpha}(e) \mid \Lambda (\alpha \isA \layout{X}).\; e
  \\
  &\tau ::= \cdots \mid X \mid \alpha \mid e\; e \mid (\alpha \isA \layout{X}) \Ra \tau
\end{align*}

>>>>

The syntactic form that introduces an SSL assertion in \PikaCore{} can be seen as a kind of binding
form, the values of which can be ``applied''. For example, $\sslmath{x, y}{x \mapsto y, (x+1) \mapsto z}$
can be seen as an SSL assertion that is parametrized over two locations: $x$ and $y$. Also, the name
$z$ occurs free. When this layout value is applied to two locations, $z$ must remain a fresh variable in
the use-site.

@@

\subsection{\Pika{} Syntax}
\begin{align*}
  &e ::= \cdots \mid \apply_{\alpha}(e) \mid \Lambda (\alpha \isA \layout{X}).\; e
  \\
  &\tau ::= \cdots \mid X \mid \alpha \mid e\; e \mid (\alpha \isA \layout{X}) \Ra \tau
\end{align*}
